### 2022-02-13 prior_versions/arxiv/proof_same_cov.tex
update

Next we present the proof of Claim \ref{claim_opt_dist}, Claim \ref{lem_exp_opt}, and Claim \ref{claim_pred_err}. 
	\begin{proof}[Proof of Claim \ref{lem_exp_opt}]
	To facilitate the analysis, we consider the following matrix notations.
	Denote
		%\[ \cE A^{\top} := {\sum_{k=1}^t \varepsilon^{(k)} A_k^{\top}}, \]
\[\cE  :=[\epsilon^{(1)},\epsilon^{(2)},\cdots, \epsilon^{(t)}],  \quad \text{ and } \quad \cW \define X(X^{\top} X)^{-1} X^{\top} \cE A^{\top} (AA^{\top})^{+}. \]
	For any $j = 1,2,\dots, t$, let
	\begin{align*}
		H_j &\define B^{\star} A^{\top} (AA^{\top})^{+} A_j - \beta^{(j)}, \quad \text{ and } \quad E_j \define \cW A_j - \varepsilon^{(j)}.
	\end{align*}
	Then we can write the function $g(A)$ conveniently as
	\[ g(A) = \sum_{j=1}^t \bignorm{X H_j + E_j}^2. \]
	We will divide $g(A)$ into three parts.
	For simplicity, we will use matrix notations in the proof, %since they are more compact.
	that is, stacking $[H_j]_j$ gives matrix $B^{\star} A^{\top} (AA^{\top}) A - B^{\star}$,
	and stacking $[E_j]_j$ gives $\cW A - \cE$.

@@

	\paragraph{Part 3:} The last part is the square of $E_j$:
	\begin{align}\label{eq_gA_p3}
		\sum_{j=1}^t \norm{E_j}^2 &= \bignormFro{\cW A - \cE}^2
		= \bignormFro{\cE}^2 - \inner{\cW A}{\cE},
	\end{align}
	where in the second step we use $\norm{\cW A}^2 = \inner{\cW A}{\cE}$ by algebraic calculation.
	Hence, it suffices to show that the expectation of equation \eqref{eq_gA_p3} is equal to $\sigma^2 (n\cdot t - p\cdot r)$.
	First, we have that $\ex{\|\cE\|_F^2} = \sigma^2 \cdot n \cdot t$.
%	Conditional on $X$, we have that
%	\begin{align*}
%		\exarg{\cE}{\norm{E_j}^2}
%		= \exarg{\cE}{\sum_{j=1}^t \bigbrace{\bignorm{\cW A_j}^2 - 2\inner{\cW A_j}{\varepsilon^{(j)}} }} + \sigma^2 \cdot n \cdot t.
%	\end{align*}
%	We consider both terms in the above equation one by one.
	Second, we show that
	%	\begin{align*}
	%		\inner{\cW A}{\cE} = \sigma^2 \cdot r \cdot \bigtr{U_X U_X^{\top}} = \sigma^2 \cdot r \cdot p,
	%	\end{align*}
	%because $U_X$ has rank $p$ by Fact \ref{lem_minv}.
	\begin{align*}
		\exarg{\cE}{ \inner{\cW A}{\cE}} =\exarg{\cE}{\bigtr{\cal E^\top U_X U_X^\top \cal E U_AU_A^\top} }= p\sigma^2 \cdot \bigtr{ U_AU_A^\top} =  p \sigma^2 \cdot r,
	\end{align*}
	where $U_XU_X^\top = X(X^{\top} X)^{-1} X^{\top}$.
	The first step follows by applying the definition of $\cW$.
	The last step is because $U_AU_A^\top$ has rank $r$.
	Hence, it suffices to show the second step is correct.
	For any $1\le i, j \le t$, let $\delta_{i, j} = 1$ if $i = j$, and $0$ otherwise.
	%\begin{align}
	%	\sum_{j=1}^t \norm{\cW A_j}^2 = \sum_{j=1}^t \bigtr{\cW A_j A_j^{\top} \cW^{\top}} = \bigtr{\cW AA^{\top} \cW^{\top}} = \bigtr{U_X U_X^{\top} \cE A^{\top} (AA^{\top})^{-1} A \cE^{\top}}. \label{eq_proof_same_cov_1}
	%\end{align}
	%We observe that
	Because $\varepsilon^{(i)}$ and $\varepsilon^{(j)}$ are pairwise independent, we have that
	\begin{align*}
			 \exarg{\cE}{(\cE^{\top}U_XU_X^\top \cE)_{ij} }
		&= \exarg{\cE}{{\varepsilon^{(i)}}^\top U_X U_X^\top  \varepsilon^{(j)} } = \sigma^2 \cdot \tr\left[U_XU_X^\top \right] \cdot \delta_{ij} = p\sigma^2 \cdot \delta_{ij}.
	\end{align*}
	The last step uses the fact that $\tr[U_XU_X^\top] = p$.
	Hence, the second step is correct.
	%Above, the second step used the fact that $\E(\varepsilon^{(i)}_k \varepsilon^{(i)}_l )=\sigma^2\cdot \delta_{ij}\delta_{kl}$ for $1\le k,l \le n$, and the third step used the fact that $\tr(U_XU_X^\top) =\tr(U_X^\top U_X) =p$.
	%Next, note that
	%\[ \sum_{j=1}^t \inner{\cW A_j}{\varepsilon^{(j)}} = \bigtr{\cW A\cE^{\top}}, \]
	%which is equal to equation \eqref{eq_proof_same_cov_1} by the definition of $\cW$.

@@

	\iffalse
	Second, notice that
	%\begin{align}
	%	\sum_{j=1}^t \norm{\cW A_j}^2 = \sum_{j=1}^t \bigtr{\cW A_j A_j^{\top} \cW^{\top}} = \bigtr{\cW AA^{\top} \cW^{\top}} = \bigtr{U_X U_X^{\top} \cE A^{\top} (AA^{\top})^{-1} A \cE^{\top}}. \label{eq_proof_same_cov_1}
	%\end{align}
	%We observe that
	\begin{align*}
			\exarg{\cE}{\cE A^{\top} (AA^{\top})^{+} A \cE^{\top}}
		&= \exarg{\cE}{\sum_{j=1}^t \sum_{k=1}^t \varepsilon^{(j)} A_j^{\top} (AA^{\top})^{+} A_k {\varepsilon^{(k)}}^{\top}} \\
		&= \exarg{\cE}{\sum_{j=1}^t \varepsilon^{(j)} A_j^{\top} (AA^{\top})^{+} A_j {\varepsilon^{(j)}}^{\top}} \\
		&= \sigma^2 \cdot r \cdot \id_{n\times n}.
	\end{align*}
	In the above derivation, the second step used the fact that for any $j\neq k$, $\varepsilon^{(j)}$ and $\varepsilon^{(k)}$ are pairwise independent.
	The third step used the fact that $\sum_{j=1}^t A_j^{\top} (AA^{\top})^{+} A_j = \bigtr{\id_{r\times r}} = r$, and $\ex{\varepsilon^{(j)} {\varepsilon^{(j)}}^{\top}} = \sigma^2 \cdot \id_{n\times n}$.
	Therefore, we have that
	\begin{align*}
		\exarg{\cE}{ \inner{\cW A}{\cE}} = \sigma^2 \cdot r \cdot \bigtr{X(X^{\top} X)^{-1} X^{\top}} =  \sigma^2 \cdot r \cdot \bigtr{ X^{\top}X(X^{\top} X)^{-1}}  = \sigma^2 \cdot r \cdot p.
	\end{align*}
   because $X^\top X$ is a $p\times p$ matrix.	
	%Next, note that
	%\[ \sum_{j=1}^t \inner{\cW A_j}{\varepsilon^{(j)}} = \bigtr{\cW A\cE^{\top}}, \]
	%which is equal to equation \eqref{eq_proof_same_cov_1} by the definition of $\cW$.
	Hence the proof is complete.
\fi

	\begin{proof}[Proof of Claim \ref{claim_opt_dist}]
	Corresponding to the right-hand side of \eqref{eq_gA}, we define the function
	\be\label{same_hA}h(A):= n \bignormFro{\Sigma^{1/2} B^{\star} \bigbrace{A^{\top} (AA^{\top})^{+} A - \id_{t\times t}}}^2 + \sigma^2 (n\cdot t - p \cdot r).\ee
	Let $\e$ be a fixed constant that is sufficiently small.
	Let $c_{\infty}$ be any fixed value within $(0, 1/2 - \e)$.
	To show that $U_{\hat{A}}U_{\hat{A}}^\top$ is close to $A^\star {A^\star}^\top$, we first show that $g(A)$ is close to $h(A)$ as follows:
	\begin{align}\label{eq_gA_err}
		\bigabs{g(A) - h(A)} \lesssim  n^{-c_{\varphi}} \cdot n \bignorm{\Sigma^{1/2} B^{\star} (U_AU_A^{\top} - \id_{t\times t})}_F^2 + n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t.
	\end{align}
%	\begin{align}\label{eq_gA_err}
%		\bigabs{g(A) - \exarg{\cE, X}{g(A)}} \lesssim p^{-c_{\varphi}} \cdot n \bignorm{\Sigma^{1/2} B^{\star} (U_AU_A^{\top} - \id)}^2 + p^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t.
%	\end{align}
	We consider the concentration error of each part of $g(A)$.

	For equation \eqref{eq_gA_p1}, % $g_0(\cal W)= \sum_{j=1}^t\left\|Z v_j \right\|^2$.
%	$$g_0(\cal W)= \sum_{j=1}^t\left\|Z v_j \right\|^2,\quad v_j:= \Sigma^{1/2}\left(B^{\star} \cW^{\top} (\cW\cW^{\top})^{-1} W_j -  \beta_j\right).$$
%	note that $X H_j = Z \Sigma^{1/2} H_j \in \real^n$ is a random vector with i.i.d. entries of mean zero, variance $\|\Sigma^{1/2}H_j\|^2$, and finite $\varphi$-th moment by Assumption \eqref{assume_rm}.
%	Hence by the law of large numbers, we have that with high probability	
	applying Corollary \ref{cor_largedeviation} to $X H_j = Z \Sigma^{1/2} H_j$, we obtain that 
	${\left\|Z \Sigma^{1/2} H_j \right\|^2 } = { n \|\Sigma^{1/2} H_j\|^2} \cdot (1 + \OO(n^{-c_\varphi}))$ with high probability. 
	This implies that
	\begin{align}
		\abs{\sum_{j=1}^t \|X H_j\|^2 -  \sum_{j=1}^t n\norm{\Sigma^{1/2} H_j}^2} \lesssim   n^{-c_{\varphi}} \cdot n  \bignorm{\Sigma^{1/2} B^{\star} (U_{A}U_A^{\top} - \id_{t\times t})}^2. \label{eq_gA_err1}
	\end{align}

	For equation \eqref{eq_gA_p2}, 
	%using Lemma \ref{largedeviation} in Appendix \ref{app_tool} and the fact that all moments of $\varepsilon_i$ exist by Assumption \eqref{assmAhigh2}, 
	using Corollary \ref{cor_calE}, we obtain the following with high probability:
	\begin{align}
		|\inner{XB^{\star} (U_AU_A^{\top} - \id_{t\times t})}{\cE}| &\le n^\e \cdot \sigma \cdot \bignormFro{XB^{\star} (U_AU_A^{\top} - \id_{t\times t})} \nonumber \\
		&\le n^{\e} \cdot \sigma \cdot \norm{Z} \cdot \bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})} \nonumber \\
		&\lesssim n^{\e + 1/2} \cdot \sigma \cdot \bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})} . \label{eq_gA_err2}
%		&\le  n^{c_\infty +c} \cdot \bignorm{\Sigma^{1/2} B^{\star} (U_AU_A^{\top} - \id_{t\times t})}^2 + n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t.
	\end{align}
	In the second step, we use the fact that $X=Z\Sigma^{1/2}$.
	In the third step, we use Fact \ref{fact_minv}(ii) to bound the operator norm of $Z$ by $\OO(\sqrt{n})$.
	By the AM-GM inequality, equation \eqref{eq_gA_err2} is bounded by the right-hand side of \eqref{eq_gA_err}.

	For equation \eqref{eq_gA_p3}, using Corollary \ref{cor_calE},
	%Lemma \ref{largedeviation} and the fact that all moments of $\varepsilon_i$ exist, 
	we obtain that with high probability,
	\begin{align}
		\abs{\normFro{\cE}^2 - \sigma^2 \cdot n \cdot t}=\abs{\tr\left[ \cal E^\top \id_{n\times n}\cal E\right] - \sigma^2 \cdot n \cdot t} &\le n^{c} \cdot \sigma^2 \| \id_{n\times n}\|_F
		= n^{1/2+c} \cdot \sigma^2. \label{eq_gA_err3}
	\end{align}
	For the inner product between $\cW A$ and $\cE$, we have that with high probability,
	\begin{align}
		\bigabs{\inner{\cW A}{\cE} - \sigma^2\cdot p \cdot r } &= \bigabs{\bigtr{\left(\cE^\top U_X U_X^{\top}\cE  - p\sigma^2 \cdot  \id_{t\times t} \right)  U_AU_A^{\top} }} \nonumber  \\
		&\le \bignormFro{U_{A} U_A^{\top}} \cdot \bignorm{\cE^\top U_X U_X^{\top} \cE - p \sigma^2 \cdot  \id_{t\times t}} \nonumber \\
		&\le \sqrt{r} \cdot n^{\e}\cdot \sigma^2\cdot \|U_X U_X^\top\|_F \nonumber \\
		&\le \sqrt{r} \cdot n^{1/2+c} \cdot \sigma^2. \label{eq_gA_err4} %  \le  n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t.
	\end{align}
	Here in the third step, we apply equation \eqref{vcalA2} to $\bignorm{\cE^\top U_X U_X^{\top} \cE - p \sigma^2 \cdot  \id_{t\times t}}$ and use that $ \bignormFro{U_{A} U_A^{\top}}=\sqrt{r}$ because $U_A$ has rank $r$. In the fourth step, we use $\|U_X U_X^\top\|_F=\sqrt{p}$ because $U_X$ has rank $p$.

@@

	\medskip
	Next, we use equation \eqref{eq_gA_err} to prove the claim.
	Using triangle inequality, we upper bound the gap between $h(A^{\star})$ and $h(\hat{A})$:  
	\begin{align}
		h(\hat{A})- h(A^{\star})   &\le \bigabs{g(A^{\star}) - h(A^{\star})} + (g(\hat A) - g({A}^{\star})) + \big|g(\hat{A}) - h(\hat{A})\big| \nonumber \\
		&\le \bigabs{g(A^{\star}) - h(A^{\star})}  + \big|g(\hat{A}) - h(\hat{A})\big|\nonumber \\
		&\lesssim n^{-c_\varphi}\cdot n \bignormFro{\Sigma^{1/2} B^{\star}}^2 + n^{-c_\infty}\cdot \sigma^2 \cdot n \cdot t. \label{eq_g_gap}
	\end{align}
	The second step used the fact that $\hat A$ is the global minimizer of $g(\cdot)$, so that $g(\hat A) \le g({A}^\star)$.
	The third step used equation \eqref{eq_gA_err} and the fact that the spectral norm of $U_A U_A^{\top} - \id_{t\times t}$ is at most one. 
	%With \eqref{eq_g_gap}, we can derive an upper bound on $\bignormFro{A^{\star} {A^{\star}}^{\top}- U_{\hat{A}} U_{\hat{A}}^{\top}}$ as follows. 
	Using equation \eqref{same_hA}, we can verify that
	$$h(\hat A)-h(A^\star) = n \bigtr{{B^\star}^\top\Sigma B^\star ( A^\star {A^\star}^\top -U_{\hat A}U^\top_{\hat A})} .$$
	Let $\lambda_1\ge\lambda_2 \ge \cdots\ge \lambda_t$ be the eigenvalues of ${B^\star}^\top\Sigma B^\star$.
	Let $v_i$ be the corresponding eigenvector of $\lambda_i$.
	Then, we have $A^\star {A^\star}^\top =\sum_{i=1}^r v_i v_i^\top$, and
	\begin{align}
	h(\hat A)-h(A^\star) = n \sum_{i=1}^r \lambda_i - n\sum_{i=1}^t \lambda_i \| U^\top_{\hat A} v_i\|^2 &= n\sum_{i=1}^r \lambda_i\left(1 -  \| U^\top_{\hat A} v_i\|^2\right)-n\sum_{i=r+1}^t \lambda_i \| U^\top_{\hat A} v_i\|^2 \nonumber\\
	&\ge  n(\lambda_r-\lambda_{r+1}) \sum_{i=r+1}^t \| U^\top_{\hat A} v_i\|^2 , \label{bdd_A-A}
	\end{align}
	where we use $\sum_{i=1}^r \left(1 -  \| U^\top_{\hat A} v_i\|^2\right) = r- \sum_{i=1}^r  \| U^\top_{\hat A} v_i\|^2 =\sum_{i=r+1}^t \| U^\top_{\hat A} v_i\|^2  $ in the last step.
	On the other hand, we have
	\begin{align*}
	\| A^\star {A^\star}^\top -U_{\hat A}U^\top_{\hat A}\|_F^2
	&= 2r - 2\inner{A^{\star}{A^{\star}}^{\top}}{U_{\hat{A}} {U_{\hat{A}}}^{\top}} \\
	&= 2 \sum_{i=r+1}^t \| U^\top_{\hat A} v_i\|^2.
	\end{align*}
	Thus from equation \eqref{eq_g_gap} and  \eqref{bdd_A-A}, we obtain that
	$$\| A^\star {A^\star}^\top -U_{\hat A}U^\top_{\hat A}\|_F^2  =2 \sum_{i=r+1}^t \| U^\top_{\hat A} v_i\|^2 \lesssim \frac{n^{-c_\varphi}\cdot  \bignormFro{\Sigma^{1/2} B^{\star}}^2 + n^{-c_\infty}\cdot \sigma^2 t}{\lambda_r- \lambda_{r+1}}  .$$
	Hence the proof is complete.
	\end{proof}

@@

	\begin{proof}[Proof of Claim \ref{claim_pred_err}]
	%We apply similar arguments from Claim \ref{lem_exp_opt} and \ref{claim_opt_dist} for this proof.
	The proof is similar to that of equation \eqref{eq_gA_err}.
	The prediction loss of hard parameter sharing for task $i$ is equal to
	\begin{align*}
		L(\hat{\beta}_i^{\MTL}) &= \bignorm{\Sigma^{1/2} (\hat{B} \hat{A}_i - \beta^{(i)})}^2 \\
		&= \bignorm{\Sigma^{1/2} ((X^{\top} X)^{-1} X^{\top} Y \hat{A}^{\top} (\hat{A} \hat{A}^{\top})^{+} \hat{A}_i - \beta^{(i)})}^2 \\
		&= \bignorm{\Sigma^{1/2} (B^{\star} \hat{a}_i - \beta^{(i)} + R_i)}^2,
	\end{align*}
	where we denote $R_i = (X^{\top} X)^{-1} X^{\top} \cE \hat{a}_i$.
	We divide the prediction loss into three parts.

>>>>

Next we present the proof of Claim \ref{claim_opt_dist}, Claim \ref{lem_exp_opt}, and Claim \ref{claim_pred_err}. 
	\begin{proof}[Proof of Claim \ref{lem_exp_opt}]
	To facilitate the analysis, we consider the following matrix notations.
	Denote
\[\cE  :=[\epsilon^{(1)},\epsilon^{(2)},\cdots, \epsilon^{(t)}],  \quad \text{ and } \quad \cW \define X(X^{\top} X)^{-1} X^{\top} \cE A^{\top} (AA^{\top})^{+}. \]
	For any $j = 1,2,\dots, t$, let
	\begin{align*}
		H_j &\define B^{\star} A^{\top} (AA^{\top})^{+} A_j - \beta^{(j)}, \quad \text{ and } \quad E_j \define \cW A_j - \varepsilon^{(j)}.
	\end{align*}
	Then we can write the function $g(A)$ conveniently as
	\[ g(A) = \sum_{j=1}^t \bignorm{X H_j + E_j}^2. \]
	We will divide $g(A)$ into three parts.
	For simplicity, we will use matrix notations in the proof, %
	that is, stacking $[H_j]_j$ gives matrix $B^{\star} A^{\top} (AA^{\top}) A - B^{\star}$,
	and stacking $[E_j]_j$ gives $\cW A - \cE$.

@@

	\paragraph{Part 3:} The last part is the square of $E_j$:
	\begin{align}\label{eq_gA_p3}
		\sum_{j=1}^t \norm{E_j}^2 &= \bignormFro{\cW A - \cE}^2
		= \bignormFro{\cE}^2 - \inner{\cW A}{\cE},
	\end{align}
	where in the second step we use $\norm{\cW A}^2 = \inner{\cW A}{\cE}$ by algebraic calculation.
	Hence, it suffices to show that the expectation of equation \eqref{eq_gA_p3} is equal to $\sigma^2 (n\cdot t - p\cdot r)$.
	First, we have that $\ex{\|\cE\|_F^2} = \sigma^2 \cdot n \cdot t$.
	Second, we show that
	\begin{align*}
		\exarg{\cE}{ \inner{\cW A}{\cE}} =\exarg{\cE}{\bigtr{\cal E^\top U_X U_X^\top \cal E U_AU_A^\top} }= p\sigma^2 \cdot \bigtr{ U_AU_A^\top} =  p \sigma^2 \cdot r,
	\end{align*}
	where $U_XU_X^\top = X(X^{\top} X)^{-1} X^{\top}$.
	The first step follows by applying the definition of $\cW$.
	The last step is because $U_AU_A^\top$ has rank $r$.
	Hence, it suffices to show the second step is correct.
	For any $1\le i, j \le t$, let $\delta_{i, j} = 1$ if $i = j$, and $0$ otherwise.
	Because $\varepsilon^{(i)}$ and $\varepsilon^{(j)}$ are pairwise independent, we have that
	\begin{align*}
			 \exarg{\cE}{(\cE^{\top}U_XU_X^\top \cE)_{ij} }
		&= \exarg{\cE}{{\varepsilon^{(i)}}^\top U_X U_X^\top  \varepsilon^{(j)} } = \sigma^2 \cdot \tr\left[U_XU_X^\top \right] \cdot \delta_{ij} = p\sigma^2 \cdot \delta_{ij}.
	\end{align*}
	The last step uses the fact that $\tr[U_XU_X^\top] = p$.
	Hence, the second step is correct.

@@

	\iffalse
	Second, notice that
	\begin{align*}
			\exarg{\cE}{\cE A^{\top} (AA^{\top})^{+} A \cE^{\top}}
		&= \exarg{\cE}{\sum_{j=1}^t \sum_{k=1}^t \varepsilon^{(j)} A_j^{\top} (AA^{\top})^{+} A_k {\varepsilon^{(k)}}^{\top}} \\
		&= \exarg{\cE}{\sum_{j=1}^t \varepsilon^{(j)} A_j^{\top} (AA^{\top})^{+} A_j {\varepsilon^{(j)}}^{\top}} \\
		&= \sigma^2 \cdot r \cdot \id_{n\times n}.
	\end{align*}
	In the above derivation, the second step used the fact that for any $j\neq k$, $\varepsilon^{(j)}$ and $\varepsilon^{(k)}$ are pairwise independent.
	The third step used the fact that $\sum_{j=1}^t A_j^{\top} (AA^{\top})^{+} A_j = \bigtr{\id_{r\times r}} = r$, and $\ex{\varepsilon^{(j)} {\varepsilon^{(j)}}^{\top}} = \sigma^2 \cdot \id_{n\times n}$.
	Therefore, we have that
	\begin{align*}
		\exarg{\cE}{ \inner{\cW A}{\cE}} = \sigma^2 \cdot r \cdot \bigtr{X(X^{\top} X)^{-1} X^{\top}} =  \sigma^2 \cdot r \cdot \bigtr{ X^{\top}X(X^{\top} X)^{-1}}  = \sigma^2 \cdot r \cdot p.
	\end{align*}
   because $X^\top X$ is a $p\times p$ matrix.	
	Hence the proof is complete.
\fi

	\begin{proof}[Proof of Claim \ref{claim_opt_dist}]
	Corresponding to the right-hand side of \eqref{eq_gA}, we define the function
	\be\label{same_hA}h(A):= n \bignormFro{\Sigma^{1/2} B^{\star} \bigbrace{A^{\top} (AA^{\top})^{+} A - \id_{t\times t}}}^2 + \sigma^2 (n\cdot t - p \cdot r).\ee
	Let $\e$ be a fixed constant that is sufficiently small.
	Let $c_{\infty}$ be any fixed value within $(0, 1/2 - \e)$.
	To show that $U_{\hat{A}}U_{\hat{A}}^\top$ is close to $A^\star {A^\star}^\top$, we first show that $g(A)$ is close to $h(A)$ as follows:
	\begin{align}\label{eq_gA_err}
		\bigabs{g(A) - h(A)} \lesssim  n^{-c_{\varphi}} \cdot n \bignorm{\Sigma^{1/2} B^{\star} (U_AU_A^{\top} - \id_{t\times t})}_F^2 + n^{-c_{\infty}} \cdot \sigma^2 \cdot n \cdot t.
	\end{align}
	We consider the concentration error of each part of $g(A)$.

	For equation \eqref{eq_gA_p1}, %
	applying Corollary \ref{cor_largedeviation} to $X H_j = Z \Sigma^{1/2} H_j$, we obtain that 
	${\left\|Z \Sigma^{1/2} H_j \right\|^2 } = { n \|\Sigma^{1/2} H_j\|^2} \cdot (1 + \OO(n^{-c_\varphi}))$ with high probability. 
	This implies that
	\begin{align}
		\abs{\sum_{j=1}^t \|X H_j\|^2 -  \sum_{j=1}^t n\norm{\Sigma^{1/2} H_j}^2} \lesssim   n^{-c_{\varphi}} \cdot n  \bignorm{\Sigma^{1/2} B^{\star} (U_{A}U_A^{\top} - \id_{t\times t})}^2. \label{eq_gA_err1}
	\end{align}

	For equation \eqref{eq_gA_p2}, 
	using Corollary \ref{cor_calE}, we obtain the following with high probability:
	\begin{align}
		|\inner{XB^{\star} (U_AU_A^{\top} - \id_{t\times t})}{\cE}| &\le n^\e \cdot \sigma \cdot \bignormFro{XB^{\star} (U_AU_A^{\top} - \id_{t\times t})} \nonumber \\
		&\le n^{\e} \cdot \sigma \cdot \norm{Z} \cdot \bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})} \nonumber \\
		&\lesssim n^{\e + 1/2} \cdot \sigma \cdot \bignormFro{\Sigma^{1/2} B^{\star}(U_AU_A^{\top} -\id_{t\times t})} . \label{eq_gA_err2}
	\end{align}
	In the second step, we use the fact that $X=Z\Sigma^{1/2}$.
	In the third step, we use Fact \ref{fact_minv}(ii) to bound the operator norm of $Z$ by $\OO(\sqrt{n})$.
	By the AM-GM inequality, equation \eqref{eq_gA_err2} is bounded by the right-hand side of \eqref{eq_gA_err}.

	For equation \eqref{eq_gA_p3}, using Corollary \ref{cor_calE},
	we obtain that with high probability,
	\begin{align}
		\abs{\normFro{\cE}^2 - \sigma^2 \cdot n \cdot t}=\abs{\tr\left[ \cal E^\top \id_{n\times n}\cal E\right] - \sigma^2 \cdot n \cdot t} &\le n^{c} \cdot \sigma^2 \| \id_{n\times n}\|_F
		= n^{1/2+c} \cdot \sigma^2. \label{eq_gA_err3}
	\end{align}
	For the inner product between $\cW A$ and $\cE$, we have that with high probability,
	\begin{align}
		\bigabs{\inner{\cW A}{\cE} - \sigma^2\cdot p \cdot r } &= \bigabs{\bigtr{\left(\cE^\top U_X U_X^{\top}\cE  - p\sigma^2 \cdot  \id_{t\times t} \right)  U_AU_A^{\top} }} \nonumber  \\
		&\le \bignormFro{U_{A} U_A^{\top}} \cdot \bignorm{\cE^\top U_X U_X^{\top} \cE - p \sigma^2 \cdot  \id_{t\times t}} \nonumber \\
		&\le \sqrt{r} \cdot n^{\e}\cdot \sigma^2\cdot \|U_X U_X^\top\|_F \nonumber \\
		&\le \sqrt{r} \cdot n^{1/2+c} \cdot \sigma^2. \label{eq_gA_err4} %
	\end{align}
	Here in the third step, we apply equation \eqref{vcalA2} to $\bignorm{\cE^\top U_X U_X^{\top} \cE - p \sigma^2 \cdot  \id_{t\times t}}$ and use that $ \bignormFro{U_{A} U_A^{\top}}=\sqrt{r}$ because $U_A$ has rank $r$. In the fourth step, we use $\|U_X U_X^\top\|_F=\sqrt{p}$ because $U_X$ has rank $p$.

@@

	\medskip
	Next, we use equation \eqref{eq_gA_err} to prove the claim.
	Using triangle inequality, we upper bound the gap between $h(A^{\star})$ and $h(\hat{A})$:  
	\begin{align}
		h(\hat{A})- h(A^{\star})   &\le \bigabs{g(A^{\star}) - h(A^{\star})} + (g(\hat A) - g({A}^{\star})) + \big|g(\hat{A}) - h(\hat{A})\big| \nonumber \\
		&\le \bigabs{g(A^{\star}) - h(A^{\star})}  + \big|g(\hat{A}) - h(\hat{A})\big|\nonumber \\
		&\lesssim n^{-c_\varphi}\cdot n \bignormFro{\Sigma^{1/2} B^{\star}}^2 + n^{-c_\infty}\cdot \sigma^2 \cdot n \cdot t. \label{eq_g_gap}
	\end{align}
	The second step used the fact that $\hat A$ is the global minimizer of $g(\cdot)$, so that $g(\hat A) \le g({A}^\star)$.
	The third step used equation \eqref{eq_gA_err} and the fact that the spectral norm of $U_A U_A^{\top} - \id_{t\times t}$ is at most one. 
	Using equation \eqref{same_hA}, we can verify that
	$$h(\hat A)-h(A^\star) = n \bigtr{{B^\star}^\top\Sigma B^\star ( A^\star {A^\star}^\top -U_{\hat A}U^\top_{\hat A})} .$$
	Let $\lambda_1\ge\lambda_2 \ge \cdots\ge \lambda_t$ be the eigenvalues of ${B^\star}^\top\Sigma B^\star$.
	Let $v_i$ be the corresponding eigenvector of $\lambda_i$.
	Then, we have $A^\star {A^\star}^\top =\sum_{i=1}^r v_i v_i^\top$, and
	\begin{align}
	h(\hat A)-h(A^\star) = n \sum_{i=1}^r \lambda_i - n\sum_{i=1}^t \lambda_i \| U^\top_{\hat A} v_i\|^2 &= n\sum_{i=1}^r \lambda_i\left(1 -  \| U^\top_{\hat A} v_i\|^2\right)-n\sum_{i=r+1}^t \lambda_i \| U^\top_{\hat A} v_i\|^2 \nonumber\\
	&\ge  n(\lambda_r-\lambda_{r+1}) \sum_{i=r+1}^t \| U^\top_{\hat A} v_i\|^2 , \label{bdd_A-A}
	\end{align}
	where we use $\sum_{i=1}^r \left(1 -  \| U^\top_{\hat A} v_i\|^2\right) = r- \sum_{i=1}^r  \| U^\top_{\hat A} v_i\|^2 =\sum_{i=r+1}^t \| U^\top_{\hat A} v_i\|^2  $ in the last step.
	On the other hand, we have
	\begin{align*}
	\| A^\star {A^\star}^\top -U_{\hat A}U^\top_{\hat A}\|_F^2
	&= 2r - 2\inner{A^{\star}{A^{\star}}^{\top}}{U_{\hat{A}} {U_{\hat{A}}}^{\top}} \\
	&= 2 \sum_{i=r+1}^t \| U^\top_{\hat A} v_i\|^2.
	\end{align*}
	Thus from equation \eqref{eq_g_gap} and  \eqref{bdd_A-A}, we obtain that
	$$\| A^\star {A^\star}^\top -U_{\hat A}U^\top_{\hat A}\|_F^2  =2 \sum_{i=r+1}^t \| U^\top_{\hat A} v_i\|^2 \lesssim \frac{n^{-c_\varphi}\cdot  \bignormFro{\Sigma^{1/2} B^{\star}}^2 + n^{-c_\infty}\cdot \sigma^2 t}{\lambda_r- \lambda_{r+1}}  .$$
	Hence the proof is complete.
	\end{proof}

@@

	\begin{proof}[Proof of Claim \ref{claim_pred_err}]
	The proof is similar to that of equation \eqref{eq_gA_err}.
	The prediction loss of hard parameter sharing for task $i$ is equal to
	\begin{align*}
		L(\hat{\beta}_i^{\MTL}) &= \bignorm{\Sigma^{1/2} (\hat{B} \hat{A}_i - \beta^{(i)})}^2 \\
		&= \bignorm{\Sigma^{1/2} ((X^{\top} X)^{-1} X^{\top} Y \hat{A}^{\top} (\hat{A} \hat{A}^{\top})^{+} \hat{A}_i - \beta^{(i)})}^2 \\
		&= \bignorm{\Sigma^{1/2} (B^{\star} \hat{a}_i - \beta^{(i)} + R_i)}^2,
	\end{align*}
	where we denote $R_i = (X^{\top} X)^{-1} X^{\top} \cE \hat{a}_i$.
	We divide the prediction loss into three parts.
